TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-02-19 article.tex
Tesis Mazzanti: reduccion de presentacion
Paper TTT: revisi'on de ilustrations con Gustavo

    \edge {d} {r};
    \edge {p1,p2} {d};
    \edge {s1} {p1};
    \edge {s2} {p2};
    %\node[invisible, right=of p2, xshift=4.35cm] (s-dist) {};
}
     \caption{
     \en{Generative model in which skills cause the observable results mediated by the difference of hidden performances, $d =p_i - p_j$, both random variables around their unknown true skill, $p \sim \N(s,\beta^2)$.}
    \es{Modelo generativo en el que las habilidades causan los resultados observables a trav\'es de la diferencia de rendimientos ocultos, $d=p_i-p_j$, ambas variables aleatorias centradas en la verdadera habilidad, $p \sim \N(s,\beta^2)$}
    %
    \en{The one with the highest performance wins, $r = (d > 0)$.}
    \es{Gana quien haya obtenido mayor rendimiento, $r = (d > 0)$.}
    %
    \en{Observable variables are painted gray, hidden in white, and constants are shown as black dots.}
    \es{Las variables observables se pintan de gris, la ocultas en blanco, y las constantes se muestran como puntos negros.}
    }
    \label{fig:generative_model}
\end{figure}
%
\en{Figure~\ref{fig:generative_model} provides a causal model in which skills generates the observable result.}
\es{La figura~\ref{fig:generative_model} ofrece un modelo causal en la que las habilidades generan el resultado observable.}
%
\en{The agents exhibit different performances at each event, varying around their true skill, $\N(p_i\,|\,s_i,\beta^2)$.}
\es{Los agentes exhiben distintos desempe\~nos en cada evento, que var\'ian alrededor de su verdadera habilidad, $\N(p\,|\,s,\beta^2)$.}
%
\en{The model assumes that the agent with the highest performance wins, $r = (p_i > p_j)$. In other words, whoever obtains a difference of performance greater than 0 wins, $r = (p_i - p_j > 0)$.}
\es{El modelo supone que gana el agente con mayor rendimiento, $r = (p_i > p_j)$, o en otras palabras, gana quien obtenga una diferencia de rendimiento mayor a 0, $r = (p_i - p_j > 0)$.}
\en{The parameter $\beta^2$ is the same for all the agents and acts as the scale of the estimations: skills separated by a $\beta$ keep always the same probability of winning.}
\es{El parámetro $\beta^2$, al ser el mismo para todos los agentes, act\'ua como la escala de las estimaciones: habilidades separada por un $\beta$ mantienen siempre la misma probabilidad de ganar.}

@@

\en{As an instance, let's consider a winning case ($p_i > p_j$) using a Gaussian prior (i.e. $\N(\,s\,|\,\mu, \sigma^2)$) for each of the skill estimations.}

@@

\en{The difference of performances, $d=p_i-p_j$, can also be expressed as a Gaussian distribution, centered on the difference of the prior estimate means ($\mu_i -\mu_j$), with a variance that incorporates the uncertainty of both estimates ($\sigma_i$ and $\sigma_j$) and the variance of both performances ($\beta$), $\N( d \, | \, \mu_i -\mu_j \, ,\ 2\beta^2 + \sigma_i^2 + \sigma_j^2 \,)$.}

@@

\es{En la primera pasada, utilizamos las versolimulitudes pasadas para calcular las priores de cada evento.}

@@

\en{TrueSkill Through Time outperforms TrueSkill and others filtering models.}
\es{TrueSkill Through Time supera a TrueSkill y otros modelos de filtrado.}
%
\en{In Figure~\ref{fig:smooth_example} we show the behavior of the estimates in a data set with two agents and two events.}
\es{En la figura~\ref{fig:smooth_example} se muestra el comportamiento de las estimaciones en conjunto de datos de dos agentes y dos eventos.}
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
    \tikz{ %
      \node[latent] (s10) {$s_{a_0}$} ;
      %
      \node[latent,  below=of s10,yshift=-1cm] (s11) {$s_{a_1}$} ;

@@

\en{In this section we show how to use \proglang{Julia}, \proglang{Python} and \proglang{R} packages to solve a single event, a short history of three events, and the real-life history of professional ATP tennis players.}
\es{En esta secci\'on mostramos c\'omo usar los usando los paquetes de\proglang{Julia}, \proglang{Python} y \proglang{R} para resolver un evento, una peque\~na historia de tres eventos y finalmente la historia real de jugadores profesional de tenis ATP.}
%
\en{We present both TrueSkill and TrueSkill Through Time solutions, and the methods to obtain the posteriors, the learning curves, and the prior prediction of the observed data (i.e. evidence).}
\es{Presentamos la soluciones TrueSkill y TrueSkill Through Time, y los m\'etodos para obtener los posteriors, las curvas de aprendizaje, y la predicci\'on a priori (i.e. evidencia) del dato observado.}
%
% \en{Finally, we make a time complexity comparison between the three packages presented in this paper and the \texttt{trueskill} package of presented in this paper \proglang{Python}.}
% \es{Por \'ultimo haremos un comparaci\'on de complejidad temporal entre los tres paquetes que presentamos en este trabajo y el paquete \texttt{trueskill} de \proglang{Python}.}
%
\en{Because we develop packages in three programming languages, by displaying code we will identify each syntax as follows.}
\es{Debido a que desarrollamos paquetes en tres lenguajes de programaci\'on, al mostrar c\'odigo identificaremos cada sintaxis del siguiente modo.}
%
\begin{lstlisting}[backgroundcolor=\color{all}, belowskip=-0.77 \baselineskip]
Syntax common to Julia, Python and R
\end{lstlisting}
\begin{paracol}{3}
\begin{lstlisting}[backgroundcolor=\color{julia}]
Julia syntax
\end{lstlisting}
  \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{python}]
Python syntax
\end{lstlisting}
   \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{r}]
R syntax
\end{lstlisting}  
\end{paracol}
%

@@

\en{To solve an event we use the class \texttt{Game()}.}
\es{Para resolver un único evento utilizamos la clase \texttt{Game()}.}
\en{To perform the analysis we first need to define the features of the players.}

@@

\en{The class \texttt{Player()} has three attributes: the prior Gaussian distribution characterized by the mean (\texttt{mu}) and the standard deviation (\texttt{sigma}); the standard deviation of the performance (\texttt{beta}); and the dynamic factor of the skill (\texttt{gamma}).}
\es{La clase \texttt{Player()} tiene tres atributos: la distribuci\'on gaussiana a priori (caracterizada por la media \texttt{mu} y el desv\'io est\'andar \texttt{sigma}); el desv\'io est\'andar de los rendimientos (\texttt{beta}); y el factor din\'amico de la habilidad (\texttt{gamma}).}
\en{Before we begin, we offer some comments on the value of the parameters.}

@@

\begin{lstlisting}[backgroundcolor=\color{all},label=lst:parameters, caption={\en{Parameters}\es{Par\'ametros}},aboveskip=0.1cm]

@@

\en{The absolute value of the mean \texttt{mu} is irrelevant because it is the difference in skills what really matters.}

@@

\en{The prior's standard deviation \texttt{sigma} must be sufficiently large so as not to leave out possible skill hypotheses.}
\es{El desvío estandar del prior \texttt{sigma} debe ser suficientemente grande para no dejar por fuera posibles hip\'otesis de habilidad.}
\en{This value depends fundamentally on the standard deviation of the performances  \texttt{beta}, which works as the scale of the estimates.}

@@

\en{A real skill difference of one $\beta$, $ s_i - s_j = \beta $, is equivalent to 76\% probability of winning whatever the value of \texttt{beta}.}

@@

\en{Being the unit of measurement of the system, we choose \texttt{beta =1.0}.}

@@

\en{The dynamic factor \texttt{gamma} is generally a small fraction of \texttt {beta}.}

@@

\en{And to initialize the draw probability \texttt{p\_draw} of the game, rule of thumb proposes to select the observed frequency of draws.}

@@

\en{These are the default values for the three packages.}
\es{Estos son los valores por defecto de los tres paquetes.}

@@

\en{In this example, we instantiate four players using the same initial parameters.}

@@

\en{The \texttt{Gaussian()} class is used to model the standard operations of Gaussian distributions including multiplication, summation, division, and substraction (details at section \ref{sec:Gasussian}).}
\es{La clase \texttt{Gaussian()} se usa para modelar las operaciones estandar de las distribuciones gaussianas, incluyendo multiplicación, suma, divisi\'on y resta (detalles en la secci\'on \ref{sec:Gaussian}).}

@@

\begin{lstlisting}[backgroundcolor=\color{white},label=lst:game, caption={\en{Initialization of teams and games}\es{Inicializaci\'on de los equipos y el juego}}, belowskip=-1.0 \baselineskip, aboveskip=0.1cm]

@@

\en{During the initialization, the class \texttt{Game()} computes the prior prediction (\texttt{evidence}) of the observed result and the approximate \texttt{likelihoods}, one for each player.}
\es{Duarante la inicialización, la clase \texttt{Game()} calcula la predicción a priori (\texttt{evidence}) del resultado observado y las verosimilitudes aproximadas (\texttt{likelihoods}), una por cada jugador.}

@@

\en{Posteriors can be found by multiplying the likelihoods and priors, or we can call the method \texttt{posteriors()} to solve it for us.}

@@

\en{The lists of likelihoods and posteriors are returned keeping the order in which players and teams were loaded during the initilization of the class \texttt{Game()}.}
\es{Las listas de verosimilitudes y posteriors se devuelven manteniendo el orden en el que los jugadores y equipos fueron cargados durante la inicialización de la clase \texttt{Game()}.}

@@

\en{Let's look at a more complex example in which the same four players participate in a game organized in 3 teams, ending with a single winning team and the losing teams tied with each other.}
\es{Veamos un ejemplo más complejo en el que los mismos cuatro jugadores participan en una partida organizados en 3 equipos, finalizando con un único equipo ganador y los equipos perdedores empatados entre sí.}
%
\en{Unlike the previous example, now we need to specify the result and the draw probability of the game.}
\es{A diferencia del ejemplo anterior, ahora necesitamos especificar el resultado y la probabilidad de empate del juego.}
%
\begin{lstlisting}[backgroundcolor=\color{white},label=lst:game, caption={\en{Initialization of teams and games}\es{Inicializaci\'on de los equipos y el juego}}, belowskip=-1.0 \baselineskip, aboveskip=0.1cm]
\end{lstlisting}
\begin{paracol}{3}
\begin{lstlisting}[backgroundcolor=\color{julia}, belowskip=-0.77 \baselineskip]
ta = [p1]
tb = [p2, p3]
tc = [p4]
teams = [ta, tb, tc]
result = [1., 0., 0.]
\end{lstlisting}
  \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{python}, belowskip=-0.77 \baselineskip]
ta = [p1]
tb = [p2, p3]
tc = [p4]
teams = [ta, tb, tc]
result = [1, 0, 0]
\end{lstlisting}
   \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{r}, belowskip=-0.77 \baselineskip]
ta = c(p1)
tb = c(p2, p3)
tc = c(p4)
teams = list(ta, tb, tc)
result = c(1, 0, 0)
\end{lstlisting}  
\end{paracol}
\begin{lstlisting}[backgroundcolor=\color{all}]
g = Game(teams, result, p_draw=0.25)
\end{lstlisting}
\todo{Revisar que se aplique gamma después de la partida.}
%
\en{where the team with the highest value beats the rest, and the teams with the same value are tied.}
\es{donde el equipo con el mayor valor le gana al resto, y los equipos con mismo valor empatan.}
%
% \en{When considering the possibility of a tie, it is necessary to indicate the approximate typical draw frequency for this type of game.}
% \es{Al considerar la posibilidad de empate se hace necesario indicar la frecuencia de empate típica aproximada que tienen ese tipo de juegos.}
%
\en{The evidence and the posteriors can be queried in the same way as before.}
\es{La evidencia y el posterior se obtienen de la misma forma que hemos visto.}

\subsection{History}

\en{The class \texttt{History()} is used to compute the posteriors and evidence of a history of events.}
\es{La clase \texttt{History()} se usa para computar los posteriors y la evidencia de una historia de eventos.}
%
\en{As an example, we initialize a history containing three players (\texttt{\small "a", "b", "c"}) and three games.}
\es{Como ejemplo, inicializamos una historia que contiene tres jugadores (\texttt{"a","b","c"}) con tres partidas.}
%
\en{In the first game \texttt{"a"} beats \texttt{"b"}, in the second game \texttt{"b"} beats \texttt{"c"}, and in the third game \texttt{"c"} beats \texttt{"a"}.}
\es{En la primera partida \texttt{"a"} le gana a \texttt{"b"}, en la segunda \texttt{"b"} le gana a \texttt{"c"} y en la tercera \texttt{"c"} le gana a \texttt{"a"}.}
%
\en{In this case, all agents win one game and lose the other.}
\es{En este caso, todos los agentes ganan una partida y pierden la otra.}
%
\begin{lstlisting}[backgroundcolor=\color{white},label=lst:history, caption={\en{History initialization}\es{Inicializaci\'on de la historia}}, belowskip=-1.0 \baselineskip, aboveskip=0.1cm]
\end{lstlisting}
\begin{paracol}{3}
\begin{lstlisting}[backgroundcolor=\color{julia},belowskip=-0.77 \baselineskip]
c1 = [["a"],["b"]]
c2 = [["b"],["c"]]
c3 = [["c"],["a"]]
composition = [c1, c2, c3]
\end{lstlisting}
  \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{python},belowskip=-0.77 \baselineskip]
c1 = [["a"],["b"]]
c2 = [["b"],["c"]]
c3 = [["c"],["a"]]
composition = [c1, c2, c3]
\end{lstlisting}
   \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{r},belowskip=-0.77 \baselineskip]
c1 = list(c("a"),c("b"))
c2 = list(c("b"),c("c"))
c3 = list(c("c"),c("a"))
composition = list(c1,c2,c3)
\end{lstlisting}
\end{paracol}
\begin{lstlisting}[backgroundcolor=\color{all}]
h = History(composition, gamma=0.0)
\end{lstlisting}
%
\en{where the variable \texttt{c1} indicates the composition of the first game using the names (i.e. identifiers) of the agents, the variable \texttt{composition} is a list containing the game compositions, and the parameter \texttt{gamma=0.0} indicate that agent's skill does not change between games.}
\es{donde la variable \texttt{c1} indica la composici\'on de la primer partida usando los nombres (i.e. identificadores) de los agentes, la variable \texttt{composition} es una lista que contiene la composición de la tres partidas y el par\'ametro \texttt{gamma=0.0} indica que la habilidad de los agetes no cambia entre partidas.}
%
\en{Again the results are implicitly defined by the order in which the game compositions were initialized: the teams appearing first in the list beat those appearing later.}
\es{Otra vez el resultado de la partida queda definido implícitamente por el orden en el que las composiciones fueron inicializadas: los equipos que aparecen primero en la lista le ganan a los que aparecen después.}
%
\en{The rest of the parameters are initialized with the default values seen in code~\ref{lst:parameters}.}
\es{El resto de los parámetros se inicializa con los valores por defecto vistos en el código \ref{lst:parameters}.}

@@

\en{To access them we can use the method \texttt{learning curves()}, which returns a dictionary that is indexed by the names of the agents.}

>>>>

    \edge {d} {r};
    \edge {p1,p2} {d};
    \edge {s1} {p1};
    \edge {s2} {p2};
    %\node[invisible, right=of p2, xshift=4.35cm] (s-dist) {};
}
     \caption{
     \en{Generative model in which skills cause the observable results mediated by the difference of hidden performances, $d =p_i - p_j$, both random variables around their unknown true skill, $p \sim \N(s,\beta^2)$.}
    \es{Modelo generativo en el que las habilidades causan los resultados observables a trav\'es de la diferencia de rendimientos ocultos, $d=p_i-p_j$, ambas variables aleatorias centradas en la verdadera habilidad, $p \sim \N(s,\beta^2)$}
    %
    \en{The one with the highest performance wins, $r = (d > 0)$.}
    \es{Gana quien haya obtenido mayor rendimiento, $r = (d > 0)$.}
    %
    \en{Observable variables are painted gray, hidden in white, and constants are shown as black dots.}
    \es{Las variables observables se pintan de gris, la ocultas en blanco, y las constantes se muestran como puntos negros.}
    }
    \label{fig:generative_model}
\end{figure}
%
\en{Figure~\ref{fig:generative_model} provides a causal model in which skills generates the observable result.}
\es{La figura~\ref{fig:generative_model} ofrece un modelo causal en la que las habilidades generan el resultado observable.}
%
\en{The agents exhibit different performances at each event, varying around their true skill, $\N(p_i\,|\,s_i,\beta^2)$.}
\es{Los agentes exhiben distintos desempe\~nos en cada evento, que var\'ian alrededor de su verdadera habilidad, $\N(p\,|\,s,\beta^2)$.}
%
\en{The model assumes that the agent with the highest performance wins, $r = (p_i > p_j)$. In other words, whoever obtains a difference of performance greater than 0 wins, $r = (p_i - p_j > 0)$.}
\es{El modelo supone que gana el agente con mayor rendimiento, $r = (p_i > p_j)$, o en otras palabras, gana quien obtenga una diferencia de rendimiento mayor a 0, $r = (p_i - p_j > 0)$.}
\en{The parameter $\beta^2$ is the same for all the agents and acts as the scale of the estimates: skills separated by a $\beta$ keep always the same probability of winning.}
\es{El parámetro $\beta^2$, al ser el mismo para todos los agentes, act\'ua como la escala de las estimaciones: habilidades separada por un $\beta$ mantienen siempre la misma probabilidad de ganar.}

@@

\en{As an instance, let's consider a winning case ($p_i > p_j$) using a Gaussian prior (i.e. $\N(\,s\,|\,\mu, \sigma^2)$) for each of the skills.}

@@

\en{The difference of performances, $d=p_i-p_j$, can also be expressed as a Gaussian distribution, centered on the difference of the prior estimates ($\mu_i -\mu_j$), with a variance that incorporates the uncertainty of both estimates ($\sigma_i$ and $\sigma_j$) and the variance of both performances ($\beta$), $\N( d \, | \, \mu_i -\mu_j \, ,\ 2\beta^2 + \sigma_i^2 + \sigma_j^2 \,)$.}

@@

\es{En la primera pasada, utilizamos las verosimilitudes pasadas para calcular las priores de cada evento.}

@@

\en{TrueSkill Through Time outperforms TrueSkill and others filtering models.}
\es{TrueSkill Through Time supera a TrueSkill y otros modelos de filtrado.}
%
\en{In Figure~\ref{fig:smooth_example} we show the estimation's behavior in a data set with two agents and two events.}
\es{En la figura~\ref{fig:smooth_example} se muestra el comportamiento de las estimaciones en conjunto de datos de dos agentes y dos eventos.}
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
    \tikz{ %
      \node[latent] (s10) {$s_{a_0}$} ;
      %
      \node[latent,  below=of s10,yshift=-1cm] (s11) {$s_{a_1}$} ;

@@

\en{In this section we show how to use \proglang{Julia}, \proglang{Python} and \proglang{R} packages to solve a single event, a sequence consisting of three events, and the real-life history of professional ATP tennis players.}
\es{En esta secci\'on mostramos c\'omo usar los usando los paquetes de\proglang{Julia}, \proglang{Python} y \proglang{R} para resolver un evento, una peque\~na historia de tres eventos y finalmente la historia real de jugadores profesional de tenis ATP.}
%
\en{We present both TrueSkill and TrueSkill Through Time solutions, and the steps to obtain the posteriors, the learning curves, and the prior prediction of the observed data (i.e. evidence).}
\es{Presentamos la soluciones TrueSkill y TrueSkill Through Time, y los m\'etodos para obtener los posteriors, las curvas de aprendizaje, y la predicci\'on a priori (i.e. evidencia) del dato observado.}
%
% \en{Finally, we make a time complexity comparison between the three packages presented in this paper and the \texttt{trueskill} package of presented in this paper \proglang{Python}.}
% \es{Por \'ultimo haremos un comparaci\'on de complejidad temporal entre los tres paquetes que presentamos en este trabajo y el paquete \texttt{trueskill} de \proglang{Python}.}
%
\en{As we present three different versions of the tool using different programming languages, we select the following color convention to identify each one:}
\es{Debido a que desarrollamos paquetes en tres lenguajes de programaci\'on, al mostrar c\'odigo identificaremos cada sintaxis del siguiente modo.}
%
\begin{lstlisting}[backgroundcolor=\color{all}, belowskip=-0.77 \baselineskip]
Syntax common to Julia, Python and R
\end{lstlisting}
\begin{paracol}{3}
\begin{lstlisting}[backgroundcolor=\color{julia}]
Julia syntax
\end{lstlisting}
  \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{python}]
Python syntax
\end{lstlisting}
   \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{r}]
R syntax
\end{lstlisting}  
\end{paracol}
%
where grey is used for all the common parts of the code (i.e. same syntax in the three languages), \proglang{Julia} code is colored with pink, \proglang{Python} with cyan, and \proglang{R} with light green.

@@

\en{The class \texttt{Game} is used to model an event.}
\es{Para resolver un único evento utilizamos la clase \texttt{Game}.}
\en{The features of the players are defined within class \texttt{Player}: the prior Gaussian distribution characterized by the mean (\texttt{mu}) and the standard deviation (\texttt{sigma}), the standard deviation of the performance (\texttt{beta}), and the dynamic factor of the skill (\texttt{gamma}).}

@@

\es{La clase \texttt{Player} tiene tres atributos: la distribuci\'on gaussiana a priori (caracterizada por la media \texttt{mu} y el desv\'io est\'andar \texttt{sigma}); el desv\'io est\'andar de los rendimientos (\texttt{beta}); y el factor din\'amico de la habilidad (\texttt{gamma}).}
\en{We assign the default values to the parameters with code~\ref{lst:parameters}.}

@@

\begin{lstlisting}[backgroundcolor=\color{all},label=lst:parameters, caption={\en{Packages' default values}\es{Par\'ametros}},aboveskip=0.1cm]

@@

\en{The initial value of \texttt{mu} can be selected by the user as it does not model any feature by itself, the difference between \texttt{mu} of the different players is what really matters.}

@@

\en{The prior's standard deviation \texttt{sigma} must be sufficiently large to include all possible skill hypotheses.}
\es{El desvío est\'andar del prior \texttt{sigma} debe ser suficientemente grande para no dejar por fuera posibles hip\'otesis de habilidad.}
\en{The parameter \texttt{beta} ($\beta$) works as the scale for the estimation.}

@@

\en{A difference of one $\beta$ between two actual skills, $ s_i - s_j = \beta $, is equivalent to 76\% probability of winning independently of the chosen \texttt{beta}.}

@@

\en{The default value for \texttt{beta} is \texttt{1.0} which is also used for this example.}

@@

\en{The dynamic factor \texttt{gamma} is generally a small fraction of \texttt{beta}.}

@@

\en{The rule of thumb to initialize the draw probability (\texttt{p\_draw}) proposes to use the observed frequency of draws.}

@@

% \en{These are the default values for the three packages.}
% \es{Estos son los valores por defecto de los tres paquetes.}

@@

\en{In this example, we instantiate four players using the same initial parameters. For the first player (\texttt{p1}), we use a call to the constructor explicitly including the initial values while \texttt{p2}, \texttt{p3}, and \texttt{p4} are initialized using default values.}

@@

\en{The \texttt{Gaussian} class is used to model the standard operations of Gaussian distributions including multiplication, summation, division, and substraction (details at section \ref{sec:Gasussian}).}
\es{La clase \texttt{Gaussian} se usa para modelar las operaciones estandar de las distribuciones gaussianas, incluyendo multiplicación, suma, divisi\'on y resta (detalles en la secci\'on \ref{sec:Gaussian}).}

@@

\begin{lstlisting}[backgroundcolor=\color{white},label=lst:game, caption={\en{Initialization of teams and a game}\es{Inicializaci\'on de los equipos y el juego}}, belowskip=-1.0 \baselineskip, aboveskip=0.1cm]

@@

\en{During the initialization, the class \texttt{Game} computes the prior prediction (\texttt{evidence}) of the observed result and the approximate \texttt{likelihoods}, one for each player.}
\es{Duarante la inicialización, la clase \texttt{Game} calcula la predicción a priori (\texttt{evidence}) del resultado observado y las verosimilitudes aproximadas (\texttt{likelihoods}), una por cada jugador.}

@@

\en{Posteriors can be found by manually multiplying the likelihoods and priors, or we can call the method \texttt{posteriors()} of class \texttt{Game} to directly compute them.}

@@

\en{The lists of likelihoods and posteriors are returned keeping the order in which players and teams were loaded during the initialization of the class \texttt{Game}. HABLAR DEL RESULTADO Y DAR INTUICION.}
\es{Las listas de verosimilitudes y posteriors se devuelven manteniendo el orden en el que los jugadores y equipos fueron cargados durante la inicialización de la clase \texttt{Game}.}

@@

\en{At this point, we analyze a more complex example in which the same four players participate in a single team game. 
The players are organized in three teams of different size (two teams with only one player and the other with two players).
The result is a single winning team and a tie between the other two losing teams.}
\es{Veamos un ejemplo más complejo en el que los mismos cuatro jugadores participan en una partida organizados en 3 equipos, finalizando con un único equipo ganador y los equipos perdedores empatados entre sí.}
%
\en{Unlike the previous example, we use a draw probability different from the default.}
\es{A diferencia del ejemplo anterior, ahora necesitamos especificar el resultado y la probabilidad de empate del juego.}
%
\begin{lstlisting}[backgroundcolor=\color{white},label=lst:game, caption={\en{Game with different sized teams}\es{Inicializaci\'on de los equipos y el juego}}, belowskip=-1.0 \baselineskip, aboveskip=0.1cm]
\end{lstlisting}
\begin{paracol}{3}
\begin{lstlisting}[backgroundcolor=\color{julia}, belowskip=-0.77 \baselineskip]
ta = [p1]
tb = [p2, p3]
tc = [p4]
teams = [ta, tb, tc]
result = [1., 0., 0.]
\end{lstlisting}
  \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{python}, belowskip=-0.77 \baselineskip]
ta = [p1]
tb = [p2, p3]
tc = [p4]
teams = [ta, tb, tc]
result = [1, 0, 0]
\end{lstlisting}
   \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{r}, belowskip=-0.77 \baselineskip]
ta = c(p1)
tb = c(p2, p3)
tc = c(p4)
teams = list(ta, tb, tc)
result = c(1, 0, 0)
\end{lstlisting}  
\end{paracol}
\begin{lstlisting}[backgroundcolor=\color{all}]
g2 = Game(teams, result, p_draw=0.25)
\end{lstlisting}
%
\en{where \texttt{teams} includes all the participants in the game while \texttt{result} has the score obtained by each team following the same order used previously.
The team with the highest value is the winner and the teams with the same value are tied.
In this way you can specify any outcome of a team game including global ties.}
\es{donde el equipo con el mayor valor le gana al resto, y los equipos con mismo valor empatan.}
%
% \en{When considering the possibility of a tie, it is necessary to indicate the approximate typical draw frequency for this type of game.}
% \es{Al considerar la posibilidad de empate se hace necesario indicar la frecuencia de empate típica aproximada que tienen ese tipo de juegos.}
%
\en{The evidence and the posteriors can be queried in the same way as before.}
\es{La evidencia y el posterior se obtienen de la misma forma que hemos visto.}

\subsection{Sequence of three events}

\en{The class \texttt{History} is used to compute the posteriors and evidence of a sequence of events.}
\es{La clase \texttt{History} se usa para computar los posteriors y la evidencia de una historia de eventos.}
%
\en{In this example, we instantiate class \texttt{History} containing three players (\texttt{\small "a", "b", "c"}) and three games.}
\es{Como ejemplo, inicializamos una historia que contiene tres jugadores (\texttt{"a","b","c"}) con tres partidas.}
%
\en{In the first game \texttt{"a"} beats \texttt{"b"}, in the second game \texttt{"b"} beats \texttt{"c"}, and in the third game \texttt{"c"} beats \texttt{"a"}.}
\es{En la primera partida \texttt{"a"} le gana a \texttt{"b"}, en la segunda \texttt{"b"} le gana a \texttt{"c"} y en la tercera \texttt{"c"} le gana a \texttt{"a"}.}
%
\en{In this case, all agents win one game and lose the other.}
\es{En este caso, todos los agentes ganan una partida y pierden la otra.}
%
\begin{lstlisting}[backgroundcolor=\color{white},label=lst:history, caption={\en{History initialization}\es{Inicializaci\'on de la historia}}, belowskip=-1.0 \baselineskip, aboveskip=0.1cm]
\end{lstlisting}
\begin{paracol}{3}
\begin{lstlisting}[backgroundcolor=\color{julia},belowskip=-0.77 \baselineskip]
c1 = [["a"],["b"]]
c2 = [["b"],["c"]]
c3 = [["c"],["a"]]
composition = [c1, c2, c3]
\end{lstlisting}
  \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{python},belowskip=-0.77 \baselineskip]
c1 = [["a"],["b"]]
c2 = [["b"],["c"]]
c3 = [["c"],["a"]]
composition = [c1, c2, c3]
\end{lstlisting}
   \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{r},belowskip=-0.77 \baselineskip]
c1 = list(c("a"),c("b"))
c2 = list(c("b"),c("c"))
c3 = list(c("c"),c("a"))
composition = list(c1,c2,c3)
\end{lstlisting}
\end{paracol}
\begin{lstlisting}[backgroundcolor=\color{all}]
h = History(composition, gamma=0.0)
\end{lstlisting}
%
\en{where the variable \texttt{c1} indicates the composition of the first game using the names (i.e. identifiers) of the agents, the variable \texttt{composition} is a list containing the game compositions, and the parameter \texttt{gamma=0.0} indicate that agent's skill does not change between games.}
\es{donde la variable \texttt{c1} indica la composici\'on de la primer partida usando los nombres (i.e. identificadores) de los agentes, la variable \texttt{composition} es una lista que contiene la composición de la tres partidas y el par\'ametro \texttt{gamma=0.0} indica que la habilidad de los agetes no cambia entre partidas.}
%
\en{Again the results are implicitly defined by the order in which the game compositions were initialized: the teams appearing first in the list beat those appearing later.}
\es{Otra vez el resultado de la partida queda definido implícitamente por el orden en el que las composiciones fueron inicializadas: los equipos que aparecen primero en la lista le ganan a los que aparecen después.}
%
\en{The rest of the parameters are initialized with the default values seen in code~\ref{lst:parameters}.}
\es{El resto de los parámetros se inicializa con los valores por defecto vistos en el código \ref{lst:parameters}.}

@@

\en{To access them we can use the method \texttt{learning\_curves()}, which returns a dictionary that is indexed by the names of the agents.}
